The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-05 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}
    \centering
    \includegraphics{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equations \ref{eq:twoinfall-ifr} and \ref{eq:twoinfall-taustar}). In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

\paragraph{Two-infall} 
We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
\begin{equation}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
\end{equation}
with normalization coefficients
\begin{equation}
    N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
\end{equation}
and
\begin{equation}
    N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
\end{equation}
Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr. We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.

@@

\citet{Johnson2021-Migration}

@@

>>>>

Figure \ref{fig:sfhs} presents an overview of our model star formation histories.

\begin{figure*}
    \centering
    \includegraphics{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}). In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

\paragraph{Two-infall} 
We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
\end{equation}
In this model, the first infall produces the thick disk and the second infall produces the thin disk. The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
\begin{equation}
    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}
\end{equation}
where we take the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$ following \citet{BlandHawthornGerhard2016-MilkyWayReview}.

@@

For each star particle in VICE, \citet{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$. This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation. However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple VICE stellar populations. These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high  latitudes and large radii.

\begin{figure*}
    \centering
    \includegraphics{figures/radial_migration.pdf}
    \caption{Caption.}
    \label{fig:radial-migration}
    \script{radial_migration.py}
\end{figure*}

@@

% TODO make table with numerical scores (KL divergences, etc) for supplementary material
% TODO explain that precise statistical understanding of these scores is outside the scope of the paper
